---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  error = FALSE,
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(covidphtext)
```

# covidphtext: Utilities to Extract Text Data From COVID-19-Related Resolutions and Policies From the Philippines

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

To assess possible impact of various COVID-19 prediction models on Philippine government response, text from various resolutions, press releases and legislation has been collected using data mining approaches implemented in R. This package includes functions used for this data mining process and datasets of text that have been collected and processed for use in text analysis.

## Installation

`covidphtext` is not yet available on CRAN. It is currently in experimental development stage. Installation of `covidphtext` at this point is only possible through its development version via [GitHub](https://github.com/como-ph/covidphtext):

```{r install, echo = TRUE, eval = TRUE}
if(!require(remotes)) install.packages("remotes")
remotes::install_github("como-ph/covidphtext")
```

## Usage

### Datasets

`covidphtext` currently has 28 datasets of COVID-19-related resolutions and policies in the Philippines. These datasets are 28 resolutions made by the Inter-Agency Task Force for the Management of Emerging Infectious Diseases (IATF).

A description of the available datasets can be found [here](https://como-ph.github.io/comotext/reference/index.html#section-datasets).

A table of the ```r nrow(iatfLinks)``` IATF resolutions and the URLs to download them can be generated using the function `get_iatf_links()` as follows:

```{r usage1, echo = TRUE, eval = TRUE}
get_iatf_links()
```

The actual PDF of the IATF resolutions/s can be downloaded using the `get_iatf_pdf()` function. For example, to download IATF Resolution No. 29, the following command is issued:

```{r usage2, echo = TRUE, eval = TRUE}
get_iatf_pdf(id = 29)
```

The command downloads the PDF of the specified IATF Resolution into a temporary directory (using `tempdir()` function) and assigns it with a filename `iatfResolution` followed by the resolution number. For IATF Resolution 29, the filename is `iatfResolution29.pdf`. The output of the `get_iatf_pdf()` function is a character vector of directory path/s to downloaded PDFs as shown above. These paths can then be used when working with these files.

### Concatenating text datasets

The datasets described above can be processed and analysed on their own or as a combined corpus of text data. `covidphtext` provides convenience functions that concatenates all or specific text datasets available from the `covidphtext` package.

#### Concatenating datasets based on a specific search term

The `combine_docs` function allows the user to specify search terms to use in identifying datasets provided by the `comotext` package. The `docs` argument allows the specification of a vector of search terms to use to identify the names of datasets to concatenate. If the name/s of the datasets contain these search terms, the datasets with these name/s will be returned.

```{r usage5, echo = TRUE, eval = TRUE}
combine_docs(docs = "resolution")
```

The `combine_iatf` function is a specialised wrapper of the `combine_docs` function that specifically returns datasets containing IATF resolutions. An additional argument `res` allows users to specify which IATF resolutions to return. To get IATF resolution 10, 11, and 12, the following call to `combine_iatf` is made as follows:

```{r usage6, echo = TRUE, eval = TRUE}
combine_iatf(docs = "resolution", res = 10:12)
```

To check if only resolutions 10 to 12 have been returned:

```{r usage7, echo = TRUE, eval = TRUE}
combine_iatf(docs = "resolution", res = 10:12)[ , c("type", "id")]
```
