---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# covidphtext: Utilities to Extract Text Data From COVID-19-Related Resolutions and Policies From the Philippines

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

To assess possible impact of various COVID-19 prediction models on Philippine government response, text from various resolutions, press releases and legislation has been collected using data mining approaches implemented in R. This package includes functions used for this data mining process and datasets of text that have been collected and processed for use in text analysis.

## Installation

`covidphtext` is not yet available on CRAN. It is currently in experimental development stage. Installation of `covidphtext` at this point is only possible through its development version via [GitHub](https://github.com/como-ph/covidphtext):

```{r install, echo = TRUE, eval = FALSE}
if(!require(remotes)) install.packages("remotes")
remotes::install_github("como-ph/covidphtext")
```

## Usage

